|

### 2025-01-29 doc/paper.qmd
prep upd

@@

If a firm had missing values for any of the Earnings Per Share Report Date fields (item5901–item5904), it did not meet the criteria set by @ball_how_2008 and was excluded from the sample. This filtering step removed 3,609,492 firm-year observations. Additionally, 5,996,793 firm-year entries were dropped because their four earnings announcements did not fall within the same calendar year. The final dataset consists of only 643,452 valid firm-year observations, starting in 1996 only, signaling the potential difference in the acocunting standards between the U.S. and Canada.

>>>>

7. To account for non-trading days in Datastream, I extend the event window from (-1, +1) to (-3, +3) to ensure the inclusion of trading days around earnings announcements.

@@

If a firm had missing values for any of the Earnings Per Share Report Date fields (item5901–item5904), it did not meet the criteria set by @ball_how_2008 and was excluded from the sample. This filtering step removed 3,609,492 missing firm-year observations. Additionally, 5,996,793 firm-year entries were dropped because their four earnings announcements did not fall within the same calendar year. The final dataset consists of only 616,980 valid firm-year observations, starting in 1996 only, signaling the potential difference in the accounting standards between the U.S. and Canada.
